Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-01 ms.qmd
trying some fixes

Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%). Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (@fig-1 B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments. In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B). While different trait categories showed different accclimation responses across habitat types, overall, they mirrored patterns seen overall (@fig-2). Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ between adult and jeuveniles (@fig-3) (Adult-Jeuvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acute_all)`; Adult-Jeuvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acclim_all)`).

@@

```{r, tbl-s1}
#| label: tbl-s1
#| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types. Models estimates are based off 1253 effect sizes from 139 studies.

@@

    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
```

#### Plots of $I^2$ for multi-level models
```{r, fig-s3}
#| label: fig-s3
#| fig-cap: I2 estimates
#| fig-align: center

>>>>

Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}_{acute}}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%). Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (@fig-1 B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments. In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B). While different trait categories showed different accclimation responses across habitat types, overall, they mirrored patterns seen overall (@fig-2). Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ between adult and jeuveniles (@fig-3) (Adult-Jeuvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acute_all)`; Adult-Jeuvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acclim_all)`).

@@

```{r, tbl-s1}
#| label: tbl-s1
#| echo: false
#| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types. Models estimates are based off 1253 effect sizes from 139 studies.

@@

    flextable(tabs1) %>% flextable::bold(part = "header") %>% flextable::autofit() %>% flextable::add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% flextable::compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
```
install.packages("flextable")
#### Plots of $I^2$ for multi-level models
```{r, fig-s3}
#| label: fig-s3
#| fig-cap: I2 estimates
#| fig-align: center
